---
title: "Lecture 3"
output: github_document
---

I'm an R Markdown document! 

# Visualization



```{r}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Scatterplots!!

create my first scatterplot
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + geom_point()
```

new approach, same plot 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_point()
```

Save and edit a plot object

```{r}
weather_plot = 
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_point()

weather_plot + geom_point()
```

### advanced scatter plot

start qjith the same one and make it fancy
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point() + geom_smooth(se = FALSE)
```

what about the aes placement 

```{r}

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_point(aes(color = name)) + geom_smooth()
```

let's facet some things

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point(alpha = .7) + geom_smooth(se = FALSE, size = 2) + facet_grid(. ~ name)
```

let's combine some elements and try a new plot

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name, size = prcp)) + geom_point(alpha = .5) + geom_smooth(se = FALSE) + facet_grid(. ~ name)
```

## some small notes

how many geoms have to exist
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_smooth(se = FALSE)
```

you can use a neat geom!
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_density2d()
```

# Univariate plots

Histograms

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) + geom_histogram()
```

can we add color?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + geom_histogram() + facet_grid(. ~ name)
```

let's try a new geometry

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + geom_density(alpha = .40)
```

what about box plots 
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) + geom_boxplot()
```

trendy plots

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + geom_violin() + stat_summary(fun = median)
```

ridge plots

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) + geom_density_ridges()
```


save and embed

```{r}
weather_plot =
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point(alpha = .5)

ggsave("weather_plot.pdf", weather_plot)
```

what about embedding

```{r}
weather_plot
```

